Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-16 03_Prep_data.Rmd
improvements to code flow and improved the retention of some data

```{r load_libraries, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, agricolae, lme4
)
```

```{r import_data}
source("R/import_data.R")
PM_MB_means <- import_data()

@@

@@

```{r simpler_clusters_REMOVE}
slimmer_PM_dat <-
   slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]

@@

```{r}
slimmer_PM_dat %>%
   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
   geom_boxplot()
```

>>>>

```{r load_libraries, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here
)
```

```{r import_data}
PM_MB_means <- read.csv("cache/1911_PM_MB_means&Ygains.csv")

@@

The trials `r unique(PM_MB_means[is.na(PM_MB_means$AUDPC_m),"trial_ref"]) `Some trials don't have an estimate of AUDPC and need to be filled in. 
The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.

```{r}
source(here("R/AUDPC_for_single_obs.R"))

@@

```{r simpler_clusters_remove}
slimmer_PM_dat <-
   slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]

@@

```{r}
slimmer_PM_dat %>%
   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
   geom_boxplot()

slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),]
```
